<a id="adt_top"></a>  

```{r adt_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
adt_module_version <- "1.0.0"

stm("Beginning ADT module")
```  

#### Contents

##### [Session Preparation](#adt_session_prep)  
##### [Split Violin Plot](#adt_split_violin_plot)  
##### [UMAP clustering for ADTs](#adt_well_umap_clustering) 
- [UMAP clustering for ADTs by Well](#adt_umap_bywell) 
- [UMAP clustering for ADTs by ADT](#adt_umap_byadt)  

##### [ADT UMIs plot](#adt_well_umi_plot)

<a id="adt_session_prep"></a>
  
#### Session Preparation  

<details style="color: lightgray;">  
  <summary>Expand output</summary>   
  
##### Load Libraries
```{r adt_load libraries}
quiet_library <- function(...) {
  suppressPackageStartupMessages(library(...))
}
quiet_library(ggplot2)
quiet_library(Seurat)
quiet_library(viridis)
quiet_library(dplyr)
quiet_library(plyr)
quiet_library(data.table)
```

##### Locate input files
```{r adt_locate input files}
stm("Identifying files for ADT analysis")

# Input directory in_adt should be defined in the parent Rmarkdown report.
if(is.null(in_adt)) {
  warning("No input directory for adt batch report, defaulting to test data")
  in_adt <- system.file("extdata/X070/adt", package = "batchreporter")
} 

adt_count_files <- list.files(in_adt,
                              pattern = "Tag_Counts.csv")

well_names <- gsub('.{15}$', '', adt_count_files)

adt_count_filepaths <- list.files(in_adt, pattern = "Tag_Counts.csv", full.names = T)
adt_pos_count_filepaths <- list.files(in_adt, pattern = "positive_tag_counts.csv", full.names = T)
adt_pos_count_files <- basename(adt_pos_count_filepaths)

cat(sprintf("IN ADT Tag Count files: \n\t%s", paste(adt_count_files, collapse = "\n\t")), sep = "\n")
stm(sprintf("IN ADT Tag Count files: \n\t%s", paste(adt_count_files, collapse = "\n\t")))  

cat(sprintf("IN POSITIVE ADT Tag Count files: \n\t%s", paste(adt_pos_count_files, collapse = "\n\t")), sep = "\n")
stm(sprintf("IN POSITIVE ADT Tag Count files: \n\t%s", paste(adt_pos_count_files, collapse = "\n\t")))

```

##### Load Inputs  
<details style="color: lightgray;"> 
  <summary>Expand output</summary>   
```{r adt_load inputs, message=F, echo=F}
count_list <- lapply(adt_count_filepaths, fread)
pos_count_list <- lapply(adt_pos_count_filepaths, fread)
pos_count_list <- lapply(pos_count_list, function(x){
  colnames(x)[1] <- "cell_barcode"
  x
})
```  


#### Create pos & neg droplet matrices, then create seurat objects
```{r adt_Create Seurat Objects, message=F, echo=F}
i = 1
seurat_list <- list()
while (i < length(count_list) + 1){
  # get top 50k negative droplets
  diff_bcs <- setdiff(count_list[[i]]$cell_barcode, pos_count_list[[i]]$cell_barcode)
  neg <- subset(count_list[[i]], subset = count_list[[i]]$cell_barcode %in% diff_bcs)
  neg <- data.frame(neg)
  neg_50k <- neg[order(neg$total, decreasing = T),]
  neg_50k <- neg_50k[1:50000,]
  rownames(neg_50k) <- neg_50k$cell_barcode
  
  # get positive cell droplets
  pos_subset <- subset(count_list[[i]], subset = count_list[[i]]$cell_barcode %in% pos_count_list[[i]]$cell_barcode)
  pos_subset <- data.frame(pos_subset)
  rownames(pos_subset) <- pos_subset$cell_barcode
  
  # create seurat objects and merge
  pos_so <- CreateSeuratObject(counts = t(pos_subset[3:length(colnames(pos_subset))]), project = 'Cells')
  neg_so <- CreateSeuratObject(counts = t(neg_50k[3:length(colnames(neg_50k))]), project = 'Empty Droplets')
  so_merge <- merge(pos_so, neg_so)
  so_merge[['well']] <- rep(well_names[i], length(so_merge@assays$RNA))
  
  # add merged object to list
  seurat_list[[i]] <- so_merge
  
  # proceed to next one
  i = i + 1
}

```  

#### Merge Seurat Objects
```{r adt_merge seurat objects}  
# all_merge <- Reduce(merge,seurat_list)

merge_seurat <- function(so_list){
  if (length(so_list) > 2){
    temp <- merge(x = so_list[[1]], y = so_list[[2]])
    i = 3
    while (i < length(so_list) + 1){
      temp <- merge(x = temp, y = so_list[[i]])
      i = i + 1
    }
    return(temp)
  }
  else{
    temp <- merge(x = so_list[[1]], y = so_list[[2]])
  }
  return(temp)
}

all_merge <- merge_seurat(seurat_list)
```  
</details>  

<a id="adt_session_prep"></a>  

#### Split Violin Plot
```{r adt_split violin plot, fig.width=12, fig.height=8, message=F, echo=F}
VlnPlot(all_merge, features = 'nCount_RNA', log = T, 
        pt.size = 0, split.plot = T, split.by = 'orig.ident', group.by = 'well') & 
  geom_hline(yintercept=1000, linetype="dashed", color = "blue") &
  geom_hline(yintercept=300, linetype="solid", color = "red") & stat_summary(fun=median, geom="point", size=2, color="green") &
  ggtitle("Count_ADT")
```  

[Return to Contents](#adt_top) 

<a id= "adt_well_umap_clustering"></a>  

#### UMAP clustering for ADTs
```{r adt_UMAP Clustering for ADTs, message=F, echo=F}
all_merge <- SetIdent(all_merge, value = 'orig.ident')
adt_positives <- subset(all_merge, idents = 'Cells')
VariableFeatures(adt_positives) <- rownames(adt_positives)

if (length(rownames(adt_positives)) > 30) {
  dims = 30
} else {
  dims = length(rownames(adt_positives)) - 1
}


adt_positives <- NormalizeData(adt_positives, normalization.method = 'CLR', margin = 2) %>% 
  ScaleData() %>% RunPCA(npcs = dims)
adt_positives <- RunUMAP(adt_positives, dims = 1:(dims)) %>% FindNeighbors(dims = 1:dims) %>% FindClusters()

```  

<a id = "adt_umap_bywell"></a>  

##### UMAP clustering ADTs by Well
```{r adt_UMAP clustering ADTs by Well, fig.width=8, fig.height=8}
DimPlot(adt_positives, group.by = 'well')
```  

[Return to Contents](#adt_top) 

```{r adt_dynamically scale adt umap height}
n_features <- length(rownames(adt_positives))
height = ceiling((n_features / 3) * 2)
```  

<a id = "adt_umap_byadt"></a>  

##### UMAP clustering for ADTs individually
```{r adt_UMAP clustering for ADTs individually, fig.width=12, fig.height=height, message=F, echo=F}
FeaturePlot(adt_positives, features = rownames(adt_positives), min.cutoff = 'q03', max.cutoff = 'q97') & 
  scale_color_viridis(option = 'inferno')
```  
[Return to Contents](#adt_top)  

#### ADT UMIs Dataframe construction - start here  
```{r ADT UMIs dataframe construction}
i = 1
colsums_list <- list()
while (i < length(count_list) + 1){
  temp_adt_so <- seurat_list[[i]]
  temp_adt_so <- SetIdent(temp_adt_so, value = 'orig.ident')
  temp_adt_positives <- subset(temp_adt_so, idents = 'Cells')
  temp_adt_pos_mtx <- t(data.frame(temp_adt_positives@assays$RNA@counts))
  colsums_df <- data.frame(colSums(temp_adt_pos_mtx))
  colnames(colsums_df) <- 'Count'
  colsums_df$ADT <- rownames(colsums_df)
  colsums_df$Well <- rep(well_names[[i]], length(rownames(colsums_df)))
  colsums_list[[i]] <- colsums_df
  i = i + 1
}

combined_colsums <- bind_rows(colsums_list, .id = "column_label")
```  
  
<a id= "adt_well_umi_plot"></a>  
  
#### ADT UMIs plot
```{r ADT UMIs plot, fig.width=12, fig.height=8}
ggplot(combined_colsums, aes(x = reorder(ADT, -Count), y = Count, color = Well)) + geom_point(size = 5) + 
  geom_hline(yintercept=median(combined_colsums$Count), linetype="dashed", color = "blue") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + scale_y_log10() 

ggplot(combined_colsums, aes(x = reorder(ADT, -Count), y = Count, color = Well)) + geom_point(size = 5) + 
  geom_hline(yintercept=median(combined_colsums$Count), linetype="dashed", color = "blue") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))  
```  
[Return to Contents](#adt_top) 

---  

ADT report module v.`r {adt_module_version}`, Zach Thomson
