<!-- # Child Rmarkdown Document for HTO QC outputs-->
<!-- Parent document must have a variable "in_dir" containing a subfolder "hto" and "rna" -->
<a id="top_cell_hashing"></a>  

```{r, include = FALSE} 
orig_workspace <- ls()

hto_module_version <- "1.0.1"  # 20211201
```

```{r include = FALSE}
hto_warning_list <- character()
# rna_in_dir <- system.file("extdata/FullBatch", package = "batchreporter")
# in_key <- system.file("extdata/example_sample_key.csv", package = "batchreporter")
#
```

The following data summarizes parsing of hash tag oligos (HTO's) per well and filtering for singlet cells based on cross-hash doublet/multiplet identification.  

### Contents 

#### [Hash Tag UMI](#hashtag_umi)
- [Pool HTO UMI Counts](#pool_hto_umi_counts)
- [Well HTO UMI Counts](#well_hto_umi_counts)
- [Well HTO UMI Counts by HTO](#well_hto_umi_counts_hto)

#### [HTO Parsing](#hto_parsing)
- [HTO Positive Cells per Well](#hto_positive_cells_well)
- [HTO Distributions](#hto_distributions)
- [HTO Cutoffs](#hto_cutoffs)
- [HTO Positivity Rate](#hto_positivity_rate)  

#### [HTO Category Summary](#hto_category_summary)  
- [Pool Hashing Summary](#pool_hashing_summary)
- [HTO Category Counts by Well](#hto_category_well)
- [HTO Category Fraction by Well](#hto_category_fraction_well)  

#### [Singlet Summaries (well-based)](#singlet_section_well)  
- [Well-Based Singlet Summary](#well_singlet_summary)
- [HTO Barcode Counts by Well](#hto_barcode_well)
- [HTO Barcode Fraction by Well](#hto_barcode_fraction_well)

#### [Singlet Summaries (hto-based)](#singlet_section_hto)  
- [Hash-Based Singlet Summary](#hto_singlet_summary)
- [Well Counts per HTO Barcode Plot](#well_hto_barcode)
- [Well Fraction per HTO Barcode Plot](#well_fraction_hto_barcode)  
  
```{r hto_warning_summary, ref.label="print_hto_warnings"} 

```  

<!-- create details section to collapse multiple no-output code blocks to save space -->
<details style="color: lightgray;">  
  <summary>Expand Code</summary> 
  
```{r hto_dependency_check, include = FALSE}
# check main rna input directory
assertthat::assert_that(exists("in_dir"), 
                        msg = "Attempting to run hto module. Missing `in_dir` variable definition")
# check hash folder exists
assertthat::assert_that(dir.exists(in_hto), 
                        msg = "Attempting to run hto module. Input `in_dir` does not contain 'hto' folder")

assertthat::assert_that(exists("in_key"),
                         msg = "Attempting to run hto module. Missing `in_key` variable definition")
assertthat::assert_that(file.exists(in_key),
                         msg = sprintf("Attempting to run hto module. Input file `in_key` [%s] does not exist", in_key))

assertthat::assert_that(exists("in_config"),
                         msg = "Attempting to run hto module. Missing `in_config` variable definition")
assertthat::assert_that(file.exists(in_config),
                         msg = sprintf("Attempting to run hto module. Input file `in_config` [%s] does not exist", in_config))

```  

```{r hto_read_config}
# Config
config_list<- batchreporter::load_config(in_config)

hash_key <- config_list$hash_key
sample_column_name <- config_list$sample_column_name

# Sample Key
df_key <- data.table::fread(in_key)

pools <- unique(df_key$PoolID)
n_pools <- length(pools)

wells <- unlist(strsplit(unique(df_key$WellID), split = ";"))
n_wells <- length(wells)

samples <- unique(df_key$SampleID)
n_samples <- length(samples)

```


```{r rna_hash_files}
# Read in all hto key to match hto names to barcodes
hto_key <- system.file(file.path("reference",hash_key), package = "HTOparser")  # Parameterize this value
in_hto_key <- fread(hto_key, header = FALSE, col.names = c("hto_barcode","hto_name")) %>% 
  mutate(hto_order = as.numeric(gsub("HT","", hto_name))) %>% 
  mutate(hto_name = factor(hto_name, levels = hto_name[order(hto_order)])) %>% # use HT number value to reorder the HT levels
  select(-hto_order)

# Read in all hto json, check expected numbers vs input well info
all_hto_json <- list.files(path = in_hto, 
                           pattern = "hto_processing_metrics.json$", 
                           full.names = TRUE, recursive = TRUE)
n_json <- length(all_hto_json)
if(n_json == 0){
  stop(sprintf("No 'hto_processing_metrics.json' files found in %s", in_hto))
} else if (n_json < n_wells){
  hto_json_warn <- sprintf("Input number of 'hto_processing_metrics.json' files (%s) is fewer than number of wells (%s) in sample key",
                           n_json, n_wells)
  warning(hto_json_warn)
  hto_warning_list <- c(hto_warning_list, hto_json_warn)
}
stm(paste0("IN HTO Processing JSON Files        :\n\t", paste(all_hto_json, collapse = "\n\t")))
cat(paste0("IN HTO Processing JSON Files        :\n\t", paste(all_hto_json, collapse = "\n\t")))

# Read in all hto matrix files, check expected numbers vs input well info
all_hto_mat <- list.files(path = in_hto, 
                           pattern = "hto_count_matrix.csv.gz$", 
                           full.names = TRUE, recursive = TRUE)
n_hto_mat <- length(all_hto_mat)
if(n_hto_mat == 0){
  stop(sprintf("No 'hto_count_matrix.csv.gz' files found in %s", in_hto))
} else if (n_hto_mat < n_wells){
  hto_mat_warn <- sprintf("Input number of 'hto_count_matrix.csv.gz' files (%s) is fewer than number of wells (%s) in sample key",
                           n_json, n_wells)
  warning(hto_mat_warn)
  hto_warning_list <- c(hto_warning_list, hto_mat_warn)
}
stm(paste0("IN HTO Matrix Files        :\n\t", paste(all_hto_mat, collapse = "\n\t")))  
cat(paste0("IN HTO Matrix Files        :\n\t", paste(all_hto_mat, collapse = "\n\t")))  

# Read in all hto metadata files, check expected numbers vs input well info
all_hto_meta <- list.files(path = in_hto, 
                           pattern = "hto_category_table.csv.gz$", 
                           full.names = TRUE, recursive = TRUE)
n_hto_meta <- length(all_hto_meta)
if(n_hto_meta == 0){
  stop(sprintf("No 'hto_category_table.csv.gz' files found in %s", in_hto))
} else if (n_hto_meta < n_wells){
  hto_meta_warn <- sprintf("Input number of 'hto_category_table.csv.gz' files (%s) is fewer than number of wells (%s) in sample key",
                           n_json, n_wells)
  warning(hto_meta_warn)
  hto_warning_list <- c(hto_warning_list, hto_meta_warn)
}
stm(paste0("IN HTO Metadata Files        :\n\t", paste(all_hto_meta, collapse = "\n\t")))
cat(paste0("IN HTO Metadata Files        :\n\t", paste(all_hto_meta, collapse = "\n\t")))

```  

```{r print_hto_warnings, eval = FALSE}
# output warnings
if(length(hto_warning_list) == 0){
    hto_warning_list <- "None"
}

simple_html_table(labels = "File Warnings", values = paste(hto_warning_list, collapse = "<br>"), col_widths_px = c(120, 600))

```

```{r hto_meta_format}  
stm("Reading in hto metadata .csv files")
hto_meta_list <- lapply(all_hto_meta, fread)
hto_meta_wells <- gsub("_.*","",basename(all_hto_meta))
hto_meta_list <- mapply(function(x,y){x$well_id <- y; x}, hto_meta_list, hto_meta_wells, SIMPLIFY = F)
hto_meta <- do.call(rbind, hto_meta_list)
rm("hto_meta_list")

hto_meta[in_hto_key, on = 'hto_barcode', hto_name := i.hto_name]  # merge in the hto names
hto_meta[ , pool_id := gsub("C\\dW\\d","", well_id)]
hto_meta[ , sample_hto:= sprintf("%s\n%s", hto_name, get(sample_column_name))]
hto_meta[ , sample_hto_pool:= sprintf("%s\n%s%s", hto_name, get(sample_column_name), pool_id)]
hto_meta[ , hto_order:=  as.numeric(gsub("HT","", hto_name))]
hto_meta[ , sample_hto_pool:=  factor(sample_hto_pool, levels = unique(sample_hto_pool[order(pool_id, hto_order)]))]
hto_meta[ , hto_order:= NULL]
hto_meta[ , hto_category:= factor(hto_category, levels = c("no_hash", "singlet", "doublet", "multiplet"))]

hto_meta_singlet <- subset(hto_meta, hto_category=="singlet")
```

```{r scrna_hash_read_json}
# Read in json files
stm("Reading in hto processing metrics json files")
well_hto_json_list <- lapply(all_hto_json, read_hto_well_json)
well_hto_json_df <- do.call(rbind, well_hto_json_list)
well_hto_json_df <- well_hto_json_df %>% 
  left_join(in_hto_key, by = "hto_barcode") %>% 
  dplyr::mutate(pool_id_short = gsub(".*-", "", gsub("C.*","", well_id))) %>% 
  dplyr::mutate(pool_id = gsub("C.*","", well_id)) %>% 
  dplyr::mutate(sample_hto = paste(hto_name, get(sample_column_name), sep = "\n")) %>% 
  dplyr::mutate(sample_hto = factor(sample_hto, levels = unique(sample_hto[order(hto_name, pool_id)]))) %>% 
  dplyr::mutate(hto_name_barcode = paste(hto_name, hto_barcode, sep = "\n")) %>%  
  dplyr::mutate(hto_name_barcode = factor(hto_name_barcode, levels = unique(hto_name_barcode[order(hto_name)]))) %>%
  dplyr::mutate(sample_pool = paste(get(sample_column_name), pool_id_short, sep = "_")) %>% 
  dplyr::mutate(sample_pool_hto = paste(sample_pool, hto_barcode, sep = "\n")) 

remove("well_hto_json_list")
```  


```{r scrna_hash_read_hash}
stm("Reading in hash matrixes from labeled h5 and multiplet h5 files")
# read in as data.table, convert to data frame with hto barcodes as rownames
hto_mat_list <- lapply(all_hto_mat, fread)

stm("Formatting hto cutoff data")
hto_mat_list <- lapply(hto_mat_list, data.frame, row.names=1)
# name the list items by well
hto_mat_wells <- gsub("_.*", "", basename(all_hto_mat))
names(hto_mat_list) <-  hto_mat_wells
# Join with metadata before merging well in case some cell barcodes are not unique
hto_df_list <- lapply(hto_mat_wells, function(x){
  mat <- data.frame(t(hto_mat_list[[x]]))
  setDT(mat, keep.rownames = "barcodes")
  to_melt <- setdiff(colnames(mat), "barcodes")
  mat <- melt(mat, id.vars ="barcodes", variable.name ="hto", 
                     value.name= "count",measure.vars = to_melt)
  mat <- mat[hto_meta, on = c("barcodes"= "cell_barcode"), `:=`(pool_id= i.pool_id, well_id=i.well_id)]
})
rm(hto_mat_list)

all_hash_fmt <- do.call(rbind, hto_df_list)
rm(hto_df_list)

# Merge in metadata
all_hash_fmt <- all_hash_fmt[hto_meta[,.(cell_barcode, well_id, pool_id, hto_barcode, hto_category)], 
                             on =c("barcodes"="cell_barcode","well_id"="well_id","pool_id"="pool_id")]
# Merge in well/hto level hashing info
all_hash_fmt <- all_hash_fmt[well_hto_json_df, on = c(hto="hto_barcode", well_id="well_id", pool_id = "pool_id")]

# Add variables for plotting hto distributions
all_hash_fmt[, log_count := ifelse(count>0, log10(count), NA)] 
all_hash_fmt[, log_cutoff := ifelse(is.na(log_count), NA, log10(cutoff))] 
all_hash_fmt[, log_count_bin := cut(log_count, 
                                      breaks = seq(min(log_count,na.rm=T), 
                                                   max(log_count,na.rm=T), 
                                                   length.out = 30))] 
# Format labels as "hash not detected" for any well/hash that has no cells with hash count >5
low_hto_cutoff <- 5
all_hash_fmt[, n_count := sum(count > low_hto_cutoff), by = .(well_id, hto)]
all_hash_fmt[, detected := n_count > 0] 
all_hash_fmt[, plot_label := ifelse(detected, "", "Hash not detected")] 

all_hash_fmt[, log_count := ifelse(detected, log_count, NA)]   # censor counts for plotting if overall hash not detected
all_hash_fmt[, log_cutoff := ifelse(detected, log_cutoff, NA)]  # censor cutoffs for plotting if overall hash not detected 

pools <- unique(all_hash_fmt$pool_id)
n_pools <- length(pools)
```  

</details>  
<!-- end of details section collapsing multiple no-output code blocks to save space -->

<a id="hashtag_umi"></a>

### Hash Tag UMI  

HTO UMI counts have been pre-filtered based on cell barcode. Only barcodes associated with cells called by CellRanger are included.  

<a id="pool_hto_umi_counts"></a>

####  Pool HTO UMI Counts
```{r umi_per_pool}
stm("Output total hto umi per pool")
pool_info <- all_hash_fmt %>%
  dplyr::group_by(pool_id) %>%
  dplyr::summarize(total_hto_umi = formatC(sum(count), big.mark = ",", digits = 0, format = "f"), .groups = "drop")
  
pool_info %>%
  gt::gt() %>%
  gt::cols_align(align = "right", columns = 2)
 
rm(pool_info)

```  

<a id="well_hto_umi_counts"></a>

####  Well HTO UMI Counts
```{r all_hto_counts, results="asis"}
stm("Output barplot total hto umi per pool")
hash_by_well <- all_hash_fmt[,.(hto_count=sum(count)), 
                             by = .(pool_id, well_id, hto, sample_pool_hto, hto_name_barcode)]

g <- ggplot(hash_by_well, aes(well_id, hto_count)) +
  geom_bar(stat="identity", fill = "blue") +
  theme_bw() +
  scale_y_continuous(labels = scales::comma) +
  guides(fill=guide_legend(title="HTO")) +
  theme(axis.text.x = element_text(angle = 90, vjust=0.5)) +
  xlab("Wells") +
  ylab("Total HTO UMI") +
  facet_wrap(~pool_id, ncol = n_pools, scales = "free_x", drop = TRUE)

tempwidth <- max(n_samples*0.5 + n_pools*0.1 + 0.2, 4)


make_subchunk(g, subchunk_name = "hto_totalumi_subchunk",quiet_knit = T,
              chunk_opt_list = list(fig.width = tempwidth, fig.height = 3))

rm(g)

```  

[Return to Contents](#top_cell_hashing) 

<a id="well_hto_umi_counts_hto"></a>

####  Well HTO UMI Counts by HTO  
```{r all_hto_counts_by_hto, , results="asis"}
stm("Output barplot total hto umi per pool per hto")
g2 <- qc_aligned_barplot_facet(hash_by_well, 
                               category_x = "well_id", 
                               name_x = "Wells", 
                               category_y = "hto_name_barcode", 
                               category_name = "hto", 
                               stat = "identity", 
                               variable_y_identity = "hto_count", 
                               name_y = "HTO UMI Counts", 
                               facet_formula = formula("~pool_id"), 
                               scales = "free_x", 
                               drop = TRUE)

tempwidth2 <- n_samples*0.5 + n_pools*0.1 + 2.2

make_subchunk(g2, subchunk_name = "hto_umibyhto_subchunk",quiet_knit = T,
              chunk_opt_list = list(fig.width = tempwidth, fig.height = 6))

rm(g2) 
```  

[Return to Contents](#top_cell_hashing) 

<a id="hto_parsing"></a>

### HTO Parsing
Showing number of cells positively associated with each hash tag for each well. Includes singlets and multiplets.  

<a id="hto_positive_cells_well"></a>

#### HTO Positive Cells per Well   
```{r hto_positive_matrix, results="asis"}
stm("Calculations for heatmap positive hto per well")
# Expected HTO per well based on input sample sheet
all_wells <- trimws(unique(unlist(strsplit(df_key$WellID, split = ";"))))
all_hto <- in_hto_key$hto_name
df_expected_hto <- expand.grid(well_id = all_wells, hto_name = all_hto) %>% 
  left_join(in_hto_key, by = "hto_name")
df_expected_hto$hto_expected <- mapply(function(x, y){any(grepl(x, df_key$WellID[df_key$HashTag == y]))},
                                   df_expected_hto$well_id, 
                                   df_expected_hto$hto_name)  


# N Cells Pos HTO per well, defined as cells above cutoff
df_expected_hto$n_positive_cells <- mapply(function(x, y){
      well_hto_json_df$n_pos[which(well_hto_json_df$well_id == x & well_hto_json_df$hto_name == y)]
    },
    df_expected_hto$well_id, 
    df_expected_hto$hto_name)
df_expected_hto$n_positive_cells[df_expected_hto$n_positive_cells <= 5] <- NA  # change to NA to color undetected tiles uniquely
if(is.list(df_expected_hto$n_positive_cells)){
  b_missing <- sapply(df_expected_hto$n_positive_cells, function(x){length(x)==0})
  b_not_missing <- !b_missing
  v_n_pos <- numeric(nrow(df_expected_hto))
  v_n_pos[b_not_missing] <- unlist(df_expected_hto$n_positive_cells[b_not_missing])
  v_n_pos[b_missing] <- NA
  df_expected_hto$n_positive_cells <- v_n_pos
}

# Flag for cells not detected
df_expected_hto$hto_detection_status <-  mapply(function(x, y){
      ifelse(x == TRUE & is.na(y),"Missing",
             ifelse(x == TRUE & !is.na(y), "Detected",
             ifelse(x == FALSE & is.na(y), "Not Used", NA)))
    },
    df_expected_hto$hto_expected, 
    df_expected_hto$n_positive_cells)

# Heat Map 
# temp_scale <- scales::rescale(c(0, 5, 1, max(df_expected_hto$n_positive_cells)))
stm("Output heatmap positive hto per well")
hm_pos <- ggplot(df_expected_hto, aes(hto_name, y=factor(well_id, levels = sort(unique(well_id), decreasing = TRUE)))) +
  geom_tile(aes(fill = n_positive_cells, color = factor(hto_detection_status, levels = c("Not Used", "Detected","Missing"))), 
            width = 0.7, height = 0.7, size = 1) +
  scale_fill_viridis_c(option = "D", na.value = "grey") +
  scale_color_manual(name = "hto_detection_status", breaks = c("Not Used", "Detected","Missing"), values = c("grey","black","red"), drop = FALSE) +
  scale_x_discrete(position = "top") +
  xlab("HTO") +
  ylab("Well") +
  facet_grid(substr(well_id,1,7) ~., drop = T, scales = "free_y")

if(!exists("n_wells")){
  wells <- unlist(strsplit(unique(df_key$WellID), split = ";"))
  n_wells <- length(wells)
}

temp_figheight <- n_wells*0.25 + 1
temp_figwidth <- length(unique(df_expected_hto$hto_name))*0.4 + 2

make_subchunk(hm_pos, subchunk_name="hto_positive_matrix_subchunk", quiet_knit = T, 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth))  
              
rm(df_expected_hto)
rm(hm_pos)

```   

[Return to Contents](#top_cell_hashing) 
  
<a id="hto_distributions"></a>

#### HTO Distributions


A specific hashtag oligo (HTO) is detected in a well when >5 cells have any raw counts. Calculated cutoffs separate cells with
background HTO count levels from cells considered positive for the HTO.  

```{r hto_ridge_hist, class.output = "superbigimage", results = "asis"}
stm("Plotting hto count ridgeplots")

get_plt_ht_temp <- function(n_well_pool, n_hto, title_label_height = 0.5, row_height_constant = 3){
    plot_height <- (n_well_pool*0.4 + row_height_constant)*ceiling(n_hto/7) + title_label_height
    return(plot_height)
}

# Censor hto if detected in <= 5 cells in the well
for (i in seq_along(pools)){
  # pool data
  df <- all_hash_fmt %>% 
    dplyr::filter(pool_id == pools[i]) %>% 
    dplyr::mutate(well_id = factor(well_id, levels = sort(unique(well_id), decreasing=T))) 
  
  # cutoff line segment
  df_lines <- df %>%
    dplyr::select(well_id, sample_hto, hto, cutoff, log_cutoff)  %>% 
    dplyr::filter(!is.na(log_cutoff)) %>% 
    dplyr::distinct() 
  
  # labels for hash not detected
  detected_labels <- df %>% 
    dplyr::select(well_id, hto, sample_hto, plot_label) %>% 
  dplyr::distinct()
  
  x_max <- max(all_hash_fmt$log_count, na.rm = T)
  x_min <- -0.1
  x_label <- (x_max - x_min)/2 + x_min

  # Plot
  g_ridge <- ggplot(df, aes(x = log_count, y = well_id)) +
    ggridges::geom_density_ridges(
                                  scale = 7, 
                                  stat = "binline",
                                  binwidth = 0.1,
                                  size = 0.5, # line width
                                  aes(color = well_id), alpha = 0,
                                  na.rm = TRUE) +
    geom_segment(data = df_lines, aes(x = log_cutoff, xend = log_cutoff,
                                      y = as.numeric(well_id), yend = as.numeric(well_id) + 0.9,
                                      linetype = "well cutoff"), 
                 color = "black", na.rm = TRUE) +
    scale_x_continuous(limits = c(x_min, x_max)) +
    scale_y_discrete(expand = c(0.01, 0)) +
    scale_linetype_manual("cutoff",values=c("well cutoff"=1)) +
    geom_text(data = detected_labels, x= x_label, 
              aes(y= as.numeric(well_id),label = plot_label), 
              size = 4, vjust = 0) +
    facet_wrap(~sample_hto, ncol = 7) +
    ggtitle(pools[i]) +
    xlab("log10(Count)") +
    ylab("Well ID") +
    theme_bw() +
    theme(axis.text.y = element_text(size = 12),
          axis.title = element_text(size = 18),
          plot.title = element_text(size = 24),
          strip.text = element_text(size = 12),
          legend.text = element_text(size = 12))
  
  # Set Height
  temp_height <- get_plt_ht_temp(n_well_pool = length(unique(df$well_id)), n_hto = length(unique(df$hto)))
  
  # Output plot with custom chunk format
  batchreporter::make_subchunk(g_ridge, subchunk_name = paste0("ridge_", i), 
                chunk_opt_list = list(fig.height = temp_height, fig.width = 18, warning = FALSE), 
                quiet_knit = TRUE)
                
  rm(df, df_lines, detected_labels, x_max, x_min, x_label, g_ridge)
}

```   

[Return to Contents](#top_cell_hashing) 

<a id="hto_cutoffs"></a>

#### HTO Cutoffs  

```{r hto_assignment, results = "asis"}
stm("Plotting hto cutoff boxplots")
g_cutoff_box <- ggplot(well_hto_json_df, aes(sample_hto, cutoff, color = hto_barcode)) +
  suppressWarnings(geom_point(alpha = 0.4, position = position_jitter(height = 0, width = 0.3, seed = 20201112),
             aes(text = sprintf("Well ID: %s",  well_id)))) +
  geom_boxplot(alpha = 0, outlier.alpha = 1, color = "black") +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(~pool_id, drop = TRUE, scales = "free_x", ncol = 2)+
  ggtitle("Well-Specific HTO Cutoffs") 

temp_figwidth <- (4*((n_pools>1)+1) + 3)
temp_figheight <- ceiling(n_pools/2)*5 + 0.4

ply_cutoff_box <- plotly::ggplotly(g_cutoff_box) %>% 
  adjust_axis_title_spacing_plotly("x", adjustment = -1.3/temp_figheight) %>%
  adjust_axis_title_spacing_plotly("y", adjustment = -0.5/temp_figwidth) %>% 
  plotly::layout(xaxis = list(title = list(text = "", standoff = 30L)),
                 yaxis = list(title = list(text = "", standoff = 20L))) 

make_subchunk(ply_cutoff_box, subchunk_name = "hto_assignment_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)
              
rm(g_cutoff_box, ply_cutoff_box)

```  
  
[Return to  Top](#top_cell_hashing)  

<a id="hto_positivity_rate"></a>

#### HTO Positivity Rate
  
```{r hto_pos_cutoff, results = "asis"}
stm("Plotting hto positive call box plots")
g_cutoff_pos <- ggplot(well_hto_json_df, aes(sample_hto, frac_pos, color = hto_barcode)) +
  suppressWarnings(geom_point(alpha = 0.4, position = position_jitter(height = 0, seed = 20201112),
             aes(text = sprintf("Well ID: %s",  well_id)))) +
  geom_boxplot(alpha = 0, outlier.alpha = 1, color = "black") +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90),
                axis.title.x = element_text(margin = margin(c(15,0,1,0)))) +
  facet_wrap(~pool_id, drop = TRUE, scales = "free_x", ncol = 2)+
  ggtitle("Fraction Positive HTO Calls per Well")

temp_figwidth <- (4*((n_pools>1)+1) + 3)
temp_figheight <- ceiling(n_pools/2)*5 + 0.4

ply_cutoff_pos <- plotly::ggplotly(g_cutoff_pos) %>% 
  adjust_axis_title_spacing_plotly("x", adjustment = -1.3/temp_figheight) %>%
  adjust_axis_title_spacing_plotly("y", adjustment = -0.5/temp_figwidth) %>% 
  plotly::layout(xaxis = list(title = list(text = "", standoff = 30L)),
                 yaxis = list(title = list(text = "", standoff = 20L))) 

make_subchunk(ply_cutoff_pos, subchunk_name = "hto_positive_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)  
              
rm(g_cutoff_pos, ply_cutoff_pos)

```  
  
[Return to Contents](#top_cell_hashing)  
    
<a id="hto_category_summary"></a>

### HTO Category Summary

<a id="pool_hashing_summary"></a>

#### Pool Hashing Summary
```{r scrna_hash_pool_summary}
stm("Output pool based summary table")
pool_summary <- hto_meta[ ,.(n_cells = .N),
                          by = .(pool_id, hto_category)]
setorder(pool_summary, pool_id, hto_category)
pool_summary[, pct_cells := round(n_cells/sum(n_cells)*100,1), by = pool_id]
setcolorder(pool_summary, c("pool_id", "hto_category", "n_cells", "pct_cells"))

qc_table(pool_summary)

rm(pool_summary)

```   
[Return to Contents](#top_cell_hashing) 

<a id="hto_category_well"></a>

#### HTO Category Counts by Well   

```{r hto_cat_counts, class.output = "superbigimage",results = "asis"}
stm("Plotting hto category counts per well")

g <- qc_aligned_barplot_facet(hto_meta,
                   category_x = "well_id",
                   name_x = "Well ID",
                   category_y = "hto_category",
                   category_name = "HTO Category",
                   colorset_y = "varibow",
                   name_y = "N Cells",
                   padding = 0.2, 
                   facet_formula = formula("~pool_id"), nrow = 1, scales = "free_x")

temp_figwidth <-  max(0.3*n_wells + 0.5*n_pools + 1.5, 4)
temp_figheight <- ceiling(n_pools/2)*4 + 0.4
make_subchunk(g, subchunk_name = "hto_cat_counts_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)  
              
rm(g)
  
```  
  
[Return to Contents](#top_cell_hashing)  
  
<a id="hto_category_fraction_well"></a>
    
### HTO Category Fraction by Well  

```{r hto_cat_fractions, class.output = "superbigimage", results="asis"}
stm("Plotting hto category fraction per well")

g <- qc_stacked_barplot_facet(hto_meta,
                       category_x = "well_id",
                       name_x = "Well ID",
                       category_y = "hto_category",
                       category_name = "HTO Category",
                       colorset_y = "varibow",
                       name_y = "Fraction of Cells",
                       as_fraction = TRUE, facet_formula = formula("~pool_id"), ncol=2, scales = "free_x") 

temp_figwidth <- max(0.3*n_wells + 0.5*n_pools + 1.5, 4)
temp_figheight <- ceiling(n_pools/2)*4 + 0.4
make_subchunk(g, subchunk_name = "hto_cat_fraction_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)

rm(g)
  
```

[Return to Contents](#top_cell_hashing)  

<a id="singlet_section_well"></a>

### Singlet Summaries (well-based)  

<a id="well_singlet_summary"></a>

#### Well-Based Summary  

<details>  
  <summary>Expand data table of summary stats by well </summary>  
  
```{r scrna_hash_well_summary}
well_summary <- hto_meta[ ,.(n_cells = .N),
                          by = .(pool_id, well_id, hto_category)]
well_summary[, pct_cells := round(n_cells/sum(n_cells)*100,1), by = c("pool_id", "well_id")]
setorder(well_summary, pool_id, well_id, hto_category)

qc_table(well_summary)

rm(well_summary)

```   

[Return to Contents](#top_cell_hashing) 

</details> 

<a id="hto_barcode_well"></a>

#### HTO Barcode Count per Well Plot  

```{r hto_counts_well, class.output = "superbigimage", results="asis"}
stm("Plotting barcode count per well and hto")

g <- qc_aligned_barplot_facet(meta = hto_meta_singlet,
                   category_x = "well_id",
                   name_x = "Well ID",
                   category_y = "sample_hto_pool",
                   category_name = "HTO/Sample",
                   colorset_y = "varibow",
                   name_y = "Number of Cells",
                   padding = 0.2,
                   facet_formula = formula("~pool_id"), nrow = 1, scales = "free", drop = TRUE) 

temp_figwidth <- max(0.3*n_wells + 0.5*n_pools + 2, 4)
temp_figheight <- ceiling(n_pools/2)*4 + 0.4
batchreporter::make_subchunk(g, subchunk_name = "hto_cat_count_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)  
              
rm(g)

```   
  
[Return to Contents](#top_cell_hashing)  

<a id="hto_barcode_fraction_well"></a>
  
#### HTO Barcode Fraction per Well Plot  

```{r hto_fraction_well, class.output = "superbigimage", results="asis"}
stm("Plotting barcode fraction per well and hto")

g <- qc_stacked_barplot_facet(meta = hto_meta_singlet,
                   category_x = "well_id",
                   name_x = "Well ID",
                   category_y = "sample_hto_pool",
                   category_name = "HTO/Sample",
                   colorset_y = "varibow",
                   name_y = "Fraction of Cells",
                   as_fraction = TRUE, 
                   facet_formula = formula("~pool_id"), nrow = 1, scales = "free_x") +
    theme(text = element_text(size = 12))

temp_figwidth <- max(0.3*n_wells + 0.5*n_pools + 1.5, 4)
temp_figheight <- ceiling(n_pools/2)*4 + 0.4
batchreporter::make_subchunk(g, subchunk_name = "hto_fraction_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)
              
rm(g)
  
```  
  
[Return to Contents](#top_cell_hashing)  

<a id="singlet_section_hto"></a>

### Singlet Summaries (hash-based)  

<a id="hto_singlet_summary"></a>

#### Hash-Based Summary  

<details>  
  <summary>Expand data table of summary stats by hash tag </summary>  
  
```{r hash_singlet_summary}
stm("Output pool based summary table")
hto_singlet_summary <- hto_meta_singlet[ ,.(n_singlet_cells = .N),
                             by = setNames(list(pool_id, hto_name, hto_barcode, get(sample_column_name)), c('pool_id', 'hto_name','hto_barcode', sample_column_name))]
setorder(hto_singlet_summary, pool_id, hto_name)
setcolorder(hto_singlet_summary, c("pool_id",sample_column_name, "hto_name", "hto_barcode", "n_singlet_cells"))

qc_table(hto_singlet_summary)

rm(hto_singlet_summary)

```  
  
[Return to Contents](#top_cell_hashing)  

</details>  

<a id="well_hto_barcode"></a> 

#### Well Count per HTO Barcode Plot  

```{r Well Count By HTO Barcode Plot, class.output = "superbigimage", results="asis"}
stm("Plotting well count per hto")

g <- qc_aligned_barplot_facet(meta = hto_meta_singlet,
                   category_x = "sample_hto_pool",
                   category_y = "well_id",
                   category_name = "Well ID",
                   name_x = "HTO/Sample",
                   colorset_y = "varibow",
                   name_y = "Number of Cells",
                   facet_formula = formula("~pool_id"), nrow = 1, scales ="free", drop = TRUE) 

temp_figwidth <- max(0.32*n_samples + 0.5*n_pools + 2, 4)
temp_figheight <- max(ceiling(n_pools/2)*((n_wells/n_pools)/3) + 0.4, 4.5)
batchreporter::make_subchunk(g, subchunk_name = "well_count_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)  
              
rm(g)

```   
  
[Return to Contents](#top_cell_hashing)  
  
<a id="well_fraction_hto_barcode"></a> 

#### Well Fraction per HTO Barcode Plot  
```{r Well Fraction By HTO Barcode Plot, class.output = "superbigimage", results="asis"}
stm("Plotting well fraction per hto")

g <- qc_stacked_barplot_facet(meta = hto_meta_singlet,
                   category_x = "sample_hto_pool",
                   category_y = "well_id",
                   category_name = "Well ID",
                   name_x = "HTO/Sample",
                   colorset_y = "varibow",
                   name_y = "Fraction of Cells",
                   as_fraction = TRUE , 
                   facet_formula = formula("~pool_id"), nrow = 1, scales ="free_x", drop = TRUE)

temp_figwidth <- max(0.32*n_samples + 0.5*n_pools + 2, 4)
temp_figheight <- ceiling(n_pools/2)*4 + 0.4
batchreporter::make_subchunk(g, subchunk_name = "well_fraction_subchunk", 
              chunk_opt_list = list(fig.height = temp_figheight, fig.width = temp_figwidth, warning = FALSE), 
              quiet_knit = TRUE)

rm(g)

```  
  
[Return to Contents](#top_cell_hashing)   

---  

HTO batch module v.`r {hto_module_version}`, Lauren Okada  

```{r hto_cleanup, include = FALSE}
module_vars <- setdiff(ls(), orig_workspace)
rm(list=module_vars)
rm(module_vars)

gc()

``` 