<a id="scatac_hashing_contents"></a>  

```{r, include = FALSE}  
orig_workspace <- ls()

scatac_hashing_module_version <- "1.0.3" #20220131
```  

### Contents

#### [Data Processing](#atac_hash_data_processing)
- [Session Preparation](#atac_hash_session_preparation)
- [Assemble Metadata](#atac_hash_assemble_meta) 

#### [QC Metrics- All Cells](#atac_hash_qc_stats)
- [ATAC vs HTO QC Categories](#atac_hash_qc_categories)
- [ATAC vs HTO Doublet Comparison](#atac_hash_doublets)

#### [QC Metrics- Singlets](#atac_hash_qc_stats_singlet)
- [Sample QC Metrics](#atac_hash_sample_stats)
- [Fragment Metrics](#atac_hash_sample_stats)
  - [Unique Fragments](#atac_hash_fragment_stats_unique)
  - [Mito. Fragments](#atac_hash_fragment_stats_mito)
  - [FRIP](#atac_hash_fragment_stats_frip)
  - [FRITSS](#atac_hash_fragment_stats_fritss)
  - [Fraction in ENCODE/Altius Index](#atac_hash_fragment_stats_fralt)

#### [Write QC JSON](#atac_hash_json_out)

#### [Session Info](#atac_hash_session_info)  

<a id="atac_hash_data_processing"></a>

### Data Processing

<a id="atac_hash_session_preparation"></a>

#### Session Preparation

<!-- begin collapsed session prep section -->
<!-- <details style="color: lightgray;">   -->
<!--   <summary>Expand session prep section</summary>    -->
  
##### Load libraries:
```{r atac_hash_Load_Libraries}
start_time_atac_hash <- Sys.time()

quiet_library <- function(...) {
  suppressPackageStartupMessages(library(...))
}
quiet_library(data.table)
quiet_library(H5weaver)
quiet_library(ggplot2)
quiet_library(cowplot)
quiet_library(jsonlite)
quiet_library(purrr)
options(stringsAsFactors = FALSE)
source('/batchreporter/R/custom_functions.R')
```

Declaring start
```{r atac_hash_Declare_start}
stm("Starting scATAC Cell Hashing Report Module")
```

##### Argument parsing  
```{r atac_hash_Parse_arguments}
if(is.null(in_atac)) {
  in_atac <- system.file("testdata/batch_qc", package = "ATAComb")
  batch_id <- "X055"
  out_dir <- tempdir()
} 

stm(paste0("IN  ATAC results dir : ", in_atac))
stm(paste0("IN  HTO dir          : ", in_hto))
stm(paste0("IN  BatchID          : ", batch_id))
stm(paste0("OUT Directory        : ", out_dir))
```

##### Input Parameters  
```{r atac_hash_Print_Arguments}
print(c(
  paste0("IN  ATAC results dir : ", in_atac),
  paste0("IN  HTO dir          : ", in_hto),
  paste0("IN  BatchID          : ", batch_id),
  paste0("OUT Directory        : ", out_dir)
))
```  
  
##### Check Input Files  
```{r atac_hash_Check_Inputs}
if(!dir.exists(in_atac)) {
  stm(paste("ERROR: Cannot find IN results dir:", in_atac))
  stop()
}  
if(!dir.exists(in_hto)) {
  stm(paste("ERROR: Cannot find IN hto dir:", in_hto))
  stop()
}
if(!dir.exists(out_dir)) {
  stm(paste("Creating output directory:", out_dir))
  dir.create(out_dir)
}
out_prefix <- file.path(out_dir, paste0(batch_id, "_"))
```  

##### Check available files  

Unfiltered metadata  
```{r}
meta_files <- list.files(in_atac, 
                         pattern = "_all_metadata.csv.gz$",
                         full.names = TRUE)
if(length(meta_files) == 0) {
  stop("Can't find unfiltered metadata files. Check input directory for *_all_metadata.csv.gz files.")
}

stm("IN Full Metadata Files:")
for(meta_file in meta_files) {
  stm(meta_file)
  print(meta_file)
}

meta_list <- map(meta_files, fread)
sample_names <- sub(".+/","",sub("_all_metadata.csv.gz","",meta_files))
names(meta_list) <- sample_names
```  

Filtered metadata  
```{r}
filt_meta_files <- list.files(in_atac, 
                         pattern = "_filtered_metadata.csv.gz$",
                         full.names = TRUE)

if(length(filt_meta_files) < length(meta_files)) {
  stop("Can't find filtered metadata files. Check input directory for *_filtered_metadata.csv.gz files.")
} else if(length(filt_meta_files) > length(meta_files)) {
  stop("Can't find all metadata files. Check input directory for *_all_metadata.csv.gz files.")
}

stm("IN Filtered Metadata Files:")
for(filt_meta_file in filt_meta_files) {
  stm(filt_meta_file)
  print(filt_meta_file)
}

filt_meta_list <- map(filt_meta_files, fread)
names(filt_meta_list) <- sub(".+/","",sub("_filtered_metadata.csv.gz","",filt_meta_files))
filt_meta_list <- filt_meta_list[sample_names]
```  
  
HTO metadata  
```{r atac_hto_dependency_check, include = FALSE}
# check hash folder exists
assertthat::assert_that(dir.exists(in_hto), 
                        msg = "Attempting to run rna quality with hto module. Input `in_dir` does not contain 'hto' folder")

assertthat::assert_that(exists("in_config"),
                         msg = "Attempting to run scATAC hashing module. Missing `in_config` variable definition")
assertthat::assert_that(file.exists(in_config),
                         msg = sprintf("Attempting to run scATAC hashing module. Input file `in_config` [%s] does not exist", in_config))

# Read in all hto metadata files, check expected numbers vs input well info
all_hto_meta <- list.files(path = in_hto, 
                           pattern = "hto_category_table.csv.gz$", 
                           full.names = TRUE, recursive = TRUE)
n_hto_meta <- length(all_hto_meta)
if(n_hto_meta == 0){
  stop(sprintf("No 'hto_category_table.csv.gz' files found in %s", in_hto))
} 
stm(paste0("IN HTO Metadata Files        :\n\t", paste(all_hto_meta, collapse = "\n\t")))
cat(paste0("IN HTO Metadata Files        :\n\t", paste(all_hto_meta, collapse = "\n\t")))

```  

Config
```{r hto_atac_read_config}
# Config
config_list<- load_config(in_config)

hash_key <- config_list$hash_key
sample_column_name <- config_list$sample_column_name

```

<!-- </details> -->
<!-- End collapsed session prep section -->

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_assemble_meta"></a>

#### Combine scATAC metadata  

<!-- begin collapsed combine metadata section -->
<!-- <details style="color: lightgray;">   -->
<!--   <summary>Expand metadata prep section</summary>    -->

```{r}
filtered_meta <- do.call(rbind, filt_meta_list)
meta <- do.call(rbind, meta_list)

cutoffs <- list(altius_frac = 0.5,
                tss_frac = 0.2,
                peaks_frac = 0.2)

meta$pass_fail <- "pass"
for(i in seq_along(cutoffs)) {
  cut_name <- names(cutoffs)[i]
  cut_val <- cutoffs[[i]]
  cut_logic <- meta[[cut_name]] <= cut_val
  meta$pass_fail[cut_logic] <- "fail"
}

meta$filtered <- meta$barcodes %in% filtered_meta$barcodes
meta$mito_frac <- meta$n_mito / meta$n_fragments
meta$well_label <- paste0(meta$well_id, "\n", meta$pbmc_sample_id)

well_samples <- unique(meta[,c("well_id","pbmc_sample_id","well_label")])
```  

##### Filter metadata based on cutoffs  
```{r}
stm("Filtering based on QC cutoffs")

meta <- meta %>%
  dplyr::left_join(dplyr::select(filtered_meta, barcodes, DoubletScore, DoubletEnrichment, TSSEnrichment), by = "barcodes")

filtered_meta <- meta
for(i in seq_along(cutoffs)) {
  cut_name <- names(cutoffs)[i]
  cut_val <- cutoffs[[i]]
  filtered_meta <- filtered_meta[filtered_meta[[cut_name]] > cut_val]
  filtered_meta <- filtered_meta[filtered_meta$filtered,]
}

filtered_meta$well_label <- paste0(filtered_meta$well_id, "\n", filtered_meta$pbmc_sample_id)

well_filtered_meta_list <- split(filtered_meta, filtered_meta$well_id)
```

Set up global metadata for reporting
```{r}
meta$barcode_category <- "fail_qc"
meta$barcode_category[!meta$filtered & meta$pass_fail == "pass"] <- "pass_doublet"
meta$barcode_category[meta$filtered & meta$pass_fail == "pass"] <- "pass_singlet"
```

[Return to Contents](#scatac_hashing_contents)

##### Format HTO metadata
```{r atac_hto_meta_format} 
stm("Reading in hto key for hashed scATAC analysis")
# Read in all hto key to match hto names to barcodes
###hto_key <- system.file(file.path("reference", hash_key), package = "HTOparser")  # Parameterize this value

in_hto_key <- fread(hto_key, header = FALSE, col.names = c("hto_barcode","hto_name")) %>% 
  mutate(hto_order = as.numeric(gsub("HT","", hto_name))) %>% 
  mutate(hto_name = factor(hto_name, levels = hto_name[order(hto_order)])) %>% # use HT number value to reorder the HT levels
  select(-hto_order) 
  
  
stm("Formatting HTO meta data") 

hto_meta_list <- lapply(all_hto_meta, fread)
hto_meta_wells <- gsub("_.*","",basename(all_hto_meta))
hto_meta_list <- mapply(function(x,y){x$well_id <- y; x}, hto_meta_list, hto_meta_wells, SIMPLIFY = F)
hto_meta <- do.call(rbind, hto_meta_list)
rm("hto_meta_list")

hto_cat_levels <- c("no_hash", "singlet", "doublet", "multiplet")
hto_meta[in_hto_key, on = 'hto_barcode', hto_name := i.hto_name]  # merge in the hto names
hto_meta[ , pool_id := gsub("C\\dW\\d","", well_id)]
hto_meta[ , sample_hto:= sprintf("%s\n%s", hto_name, get(sample_column_name))]
hto_meta[ , sample_hto_pool:= sprintf("%s\n%s%s", hto_name, get(sample_column_name), pool_id)]
hto_meta[ , hto_order:=  as.numeric(gsub("HT","", hto_name))]
hto_meta[ , sample_hto_pool:=  factor(sample_hto_pool, levels = unique(sample_hto_pool[order(pool_id, hto_order)]))]
hto_meta[ , hto_order:= NULL]
hto_meta[ , hto_category:= factor(hto_category, levels = hto_cat_levels)]

# well id to merge in hto info with atac data
hto_meta[ , atac_well_id := gsub("-P","-AP", well_id)]
hto_meta[ , atac_original_barcodes := paste0(cell_barcode, "-1")]

hto_meta_singlet <- subset(hto_meta, hto_category=="singlet")

```   
[Return to Contents](#scatac_hashing_contents)

##### Merge HTO and ATAC metadata
```{r atac_merge_hto, fig.height= 2, fig.width = 6}
stm("Merging hto data with ATAC metadata") 

# Join in hto metadata for cells in atac dataset, rename some atac variables to avoid confusion
meta_hto <- meta %>%
    dplyr::rename(pbmc_sample_id_old = pbmc_sample_id) %>%
    dplyr::rename(atac_well_id = well_id) %>%
    dplyr::mutate(atac_pool_id = gsub("C.*", "", atac_well_id)) %>%
    dplyr::left_join(hto_meta, 
                     by = c("original_barcodes"="atac_original_barcodes", "atac_well_id"),
                     suffix = c("_atac","")) %>%  # use suffix in case there are additional column overlaps in the future. 
    dplyr::mutate(pool_id=ifelse(is.na(pool_id), gsub("-A","-", atac_pool_id), pool_id))

meta_singlet <- meta_hto %>%
    filter(hto_category == "singlet")

# Full Join of hto and atac cells to compare existence between the two datasets
meta_hto_full <- meta %>%
    dplyr::rename(pbmc_sample_id_old = pbmc_sample_id) %>%
    dplyr::rename(atac_well_id = well_id) %>%
    dplyr::mutate(atac_pool_id = gsub("C.*", "", atac_well_id)) %>%
    dplyr::full_join(hto_meta, 
                     by = c("original_barcodes"="atac_original_barcodes", "atac_well_id"), 
                     suffix = c("_atac","")) %>%
    dplyr::mutate(hto_category = factor(hto_category, levels = c(hto_cat_levels, "hto_missing"))) %>%
    dplyr::mutate(hto_category = replace_na(hto_category, replace="hto_missing")) %>%
    dplyr::mutate(barcode_category = replace_na(barcode_category, replace="atac_missing")) %>%
    dplyr::mutate(pool_id=ifelse(is.na(pool_id), gsub("-A","-", atac_pool_id),pool_id))

```  
[Return to Contents](#scatac_hashing_contents)

##### Merge HTO and Filtered ATAC metadata
```{r atac_filter_merge_hto, fig.height= 2, fig.width = 6}
stm("Merging hto data with filtered ATAC metadata") 

# Join in hto metadata for cells in atac dataset, rename some atac variables to avoid confusion
filtered_meta_hto <- filtered_meta %>%
    dplyr::rename(pbmc_sample_id_old = pbmc_sample_id) %>%
    dplyr::rename(atac_well_id = well_id) %>%
    dplyr::left_join(hto_meta, by = c("original_barcodes"="atac_original_barcodes", "atac_well_id"),
                     suffix = c("_atac", "")) 

filtered_meta_singlet <- filtered_meta_hto %>%
    dplyr::filter(hto_category == "singlet")  

well_filtered_meta_singlet_list <- split(filtered_meta_singlet, filtered_meta_singlet$well_id)
sample_filtered_meta_singlet_list <- split(filtered_meta_singlet, filtered_meta_singlet$pbmc_sample_id)

```
<!-- </details>   -->
<!-- end collapsed metadata prep section -->  

[Return to Contents](#scatac_hashing_contents)  

<a id="atac_hash_qc_stats"></a>

### QC Metrics: All Cells

```{r}
qc_list <- list(report_type = "atac_batch_qc",
                report_datetime = as.character(start_time_atac_hash),
                report_uuid = ids::uuid(use_time = TRUE),
                package = "batchreporter",
                package_version = "1.1.6",
                batch_id = sub("_.+","",sample_names[1]))

out_json <- paste0(out_prefix, "atac_hashing_batch_qc_metrics.json")
```

<a id="atac_hash_qc_categories"></a>

#### ATAC vs HTO QC Categories  
Counts in "n_removed_atac" are cells in the HTO library that were filtered out in 
ATAC preprocessing for failing to meet minimal quality thresholds. 
Counts in "hto_missing" are cells in the ATAC library that were not detected in
the HTO library.  
  
```{r atac_hto_qc_cat}
stm("Generating HTO/ATAC QC Category contingency table") 

barcode_counts_htocat <- meta_hto_full[,.(n_barcodes = nrow(.SD),
                            n_pass_qc = sum(.SD$pass_fail == "pass", na.rm = T),
                            n_fail_qc = sum(.SD$pass_fail == "fail", na.rm = T),
                            n_removed_atac = sum(is.na(.SD$pass_fail)),
                            percent_fail = round(sum(.SD$pass_fail == "fail", na.rm=T)/sum(!is.na(.SD$pass_fail))*100,2),
                            pass_singlets = sum(.SD$barcode_category == "pass_singlet", na.rm=T),
                            pass_doublets = sum(.SD$barcode_category == "pass_doublet", na.rm=T),
                            percent_doublets = round(sum(.SD$barcode_category == "pass_doublet", na.rm=T)/sum(.SD$pass_fail == "pass", na.rm=T)*100,2)),
                         .(atac_well_id, hto_category)]

qc_list$barcode_stats_allhtoatac <- as.list(barcode_counts_htocat)

qc_table(barcode_counts_htocat)
```

```{r atac_hto_qc_cat_barplots, results = "asis"} 
stm("Plotting HTO/ATAC QC Category barplots") 
g1 <- qc_aligned_barplot_facet(meta_hto_full, category_x = "barcode_category", category_name = "HTO Category", 
                   category_y = "hto_category", name_y = "N Cells", 
                   name_x = "ATAC Barcode Category",colorset_y = "varibow", facet_formula = as.formula("~pool_id"))  
g2 <- qc_aligned_barplot_facet(meta_hto_full, category_x = "hto_category", category_name = "ATAC Barcode Category", 
                   category_y = "barcode_category", name_y = "N Cells", 
                   name_x = "HTO Category",colorset_y = "varibow", facet_formula = as.formula("~pool_id"))

npool <- length(unique(meta_hto_full$pool_id))
temp_figwidth <- 6*npool
temp_figheight <- 4

make_subchunk(g1, subchunk_name = "subchunk_htocat_ataccat",chunk_opt_list = list(fig.width = temp_figwidth, fig.height = temp_figheight))
make_subchunk(g2, subchunk_name = "subchunk_ataccat_htocat",chunk_opt_list = list(fig.width = temp_figwidth, fig.height=temp_figheight))

# cowplot::plot_grid(g1, g2, align = "hv", axis = "tblr")
```   
[Return to Contents](#scatac_hashing_contents)  

<a id="atac_hash_doublets"></a>

#### ATAC vs HTO Doublet Comparison  
```{r fig.height = 3, fig.width = 12} 
stm("Plotting ATAC Doublet Enrichment by HTO Categorys") 
gbox1 <- ggplot(meta_hto, aes(hto_category, DoubletEnrichment)) +
    geom_point(position = position_jitter(height = 0, width = 0.3), alpha = 0.1, aes(color = hto_category))+
    geom_boxplot(alpha = 0, outlier.alpha = 1)  +
    facet_wrap(~pool_id)

    # geom_violin(alpha = 0) + 

gbox2 <- ggplot(meta_hto, aes(hto_category, DoubletScore)) +
    geom_point(position = position_jitter(height = 0, width = 0.3), alpha = 0.1, aes(color = hto_category))+
    geom_boxplot(alpha = 0, outlier.alpha = 1)  +
    facet_wrap(~pool_id)
    # geom_violin(alpha = 0) + 

cowplot::plot_grid(gbox1, gbox2, align = "hv")

```  

<a id="atac_hash_qc_stats_singlet"></a>  

### QC Metrics: Singlet Cells  
QC stats for singlet cells as identified by hashing.  

<a id="atac_hash_sample_stats"></a>

#### Sample QC Metrics 
```{r}
barcode_counts <- meta_singlet[,.(n_barcodes = nrow(.SD),
                            n_pass_qc = sum(.SD$pass_fail == "pass"),
                            n_fail_qc = sum(.SD$pass_fail == "fail"),
                            percent_fail = round(sum(.SD$pass_fail == "fail")/nrow(.SD)*100,2),
                            pass_singlets = sum(.SD$barcode_category == "pass_singlet"),
                            pass_doublets = sum(.SD$barcode_category == "pass_doublet"),
                            percent_doublets = round(sum(.SD$barcode_category == "pass_doublet")/sum(.SD$pass_fail == "pass")*100,2)),
                         .(pool_id, pbmc_sample_id)]

qc_list$barcode_stats <- as.list(barcode_counts)

qc_table(barcode_counts)
```

```{r}
qc_stacked_barplot(meta_singlet,
                   category_x = "sample_hto_pool",
                   name_x = "Sample",
                   category_y = "barcode_category",
                   category_name = "Barcode Category",
                   as_fraction = TRUE) +
  xlab("Fraction Cells")
```

```{r}
qc_aligned_barplot_facet(meta_singlet,
                   category_x = "sample_hto_pool",
                   name_x = "Sample",
                   category_y = "barcode_category",
                   category_name = "Barcode Category", facet_formula = as.formula("~pool_id"))
```

```{r}
qc_violin_plot(filtered_meta_singlet,
               category_x = "sample_hto_pool",
               name_x = "Sample",
               column_y = "DoubletEnrichment",
               name_y = "Doublet Enrichment",
               log_y = FALSE,
               fill = "dodgerblue")
```

```{r}
qc_violin_plot(filtered_meta_singlet,
               category_x = "sample_hto_pool",
               name_x = "Sample",
               column_y = "DoubletScore",
               name_y = "Doublet Score",
               log_y = FALSE,
               fill = "dodgerblue")
```

```{r}
qc_violin_plot(filtered_meta_singlet,
               category_x = "sample_hto_pool",
               name_x = "Sample",
               column_y = "TSSEnrichment",
               name_y = "TSS Enrichment",
               log_y = FALSE,
               fill = "dodgerblue")
```
[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_fragment_stats"></a>

#### Fragment QC Metrics
Fragment QC stats for all singlet cells as determined by HTO category.  

Plot Settings
```{r}
n_grid_columns <- min(length(sample_filtered_meta_singlet_list),4)
n_grid_rows <- ceiling(length(sample_filtered_meta_singlet_list)/4)

grid_width <- n_grid_columns * 3
grid_height <- n_grid_rows * 3
```


```{r}
fragment_stats <- filtered_meta_singlet[,.(n_singlets = nrow(.SD[.SD$filtered]),
                                   med_raw_frag = round(median(n_fragments),0),
                                   med_raw_perc_mito = round(median(mito_frac)*100,4),
                                   med_unique_frag = round(median(n_unique),0),
                                   med_unique_fritss = round(median(tss_frac),4),
                                   med_unique_frip = round(median(peaks_frac),4),
                                   med_unique_encode = round(median(altius_frac),4)
                                   ),
                                .(pool_id, pbmc_sample_id)]

qc_list$fragment_stats <- as.list(fragment_stats)

qc_table(fragment_stats)
```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_fragment_stats_unique"></a>

#### Unique Fragments per Cell
```{r}
# violins for all atac data by atac category
category_reads_violins <- qc_violin_plot(meta_hto,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "n_unique",
                                         name_y = "Unique Fragments",
                                         fill = "dodgerblue")
# violins for all atac data by hto category
hto_reads_violins <- qc_violin_plot(meta_hto,
                                     category_x = "hto_category",
                                     name_x = "HTO Category",
                                     column_y = "n_unique",
                                     name_y = "Unique Fragments",
                                     fill = "dodgerblue")
well_reads_violins <- qc_violin_plot(filtered_meta_singlet,
                                     category_x = "sample_hto_pool",
                                     name_x = "Sample",
                                     column_y = "n_unique",
                                     name_y = "Unique Fragments (Singlets)",
                                     fill = "dodgerblue")

reads_violin_list <- list(category_reads_violins, 
                          hto_reads_violins,
                          well_reads_violins)

plot_grid(plotlist = reads_violin_list,
          ncol = 3, rel_widths = c(1, 1, 3), 
          nrow = 1, align = "h")
```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_fragment_stats_mito"></a>

#### Fraction of Raw Reads in Mitochondria per Cell
```{r}
category_mito_violins <- qc_violin_plot(meta_hto,
                                        category_x = "barcode_category",
                                        name_x = "Barcode Type",
                                        column_y = "mito_frac",
                                        name_y = "Fraction Mitochondrial",
                                        fill = "darkgreen",
                                        log_y = F) 

hto_mito_violins <- qc_violin_plot(meta_hto,
                                    category_x = "hto_category",
                                    name_x = "HTO Category",
                                    column_y = "mito_frac",
                                    name_y = "Fraction Mitochondrial",
                                    fill = "darkgreen",
                                    log_y = F)

sample_mito_violins <- qc_violin_plot(filtered_meta_singlet,
                                     category_x = "sample_hto_pool",
                                     name_x = "Sample",
                                     column_y = "mito_frac",
                                     name_y = "Fraction Mito. (Singlets)",
                                     fill = "darkgreen",
                                     log_y = F)

mito_violin_list <- list(category_mito_violins, 
                         hto_mito_violins,
                          sample_mito_violins)


plot_grid(plotlist = mito_violin_list,
          ncol = 3, rel_widths = c(1, 1, 3), 
          nrow = 1, align = "h")

```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_fragment_stats_frip"></a>

#### Fraction of Reads in Peaks per Cell
```{r}
category_frip_violins <- qc_violin_plot(meta_hto,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "peaks_frac",
                                         name_y = "FRIP",
                                         fill = "orangered",
                                        log_y = FALSE)
hto_frip_violins <- qc_violin_plot(meta_hto,
                                         category_x = "hto_category",
                                         name_x = "HTO Category",
                                         column_y = "peaks_frac",
                                         name_y = "FRIP",
                                         fill = "orangered",
                                        log_y = FALSE)
sample_frip_violins <- qc_violin_plot(filtered_meta_singlet,
                                     category_x = "sample_hto_pool",
                                     name_x = "Sample",
                                     column_y = "peaks_frac",
                                     name_y = "FRIP (Singlets)",
                                     fill = "orangered",
                                    log_y = FALSE)

frip_violin_list <- list(category_frip_violins, 
                         hto_frip_violins,
                         sample_frip_violins)

plot_grid(plotlist = frip_violin_list,
          ncol = 3, rel_widths = c(1, 1, 3),
          nrow = 1, align = "h")
```

#### Reads vs peaks_frac scatter
```{r fig.width=grid_width, fig.height=grid_height}
qc_scatter_list <- map(sample_filtered_meta_singlet_list,
                       function(sample_meta) {
                         qc_scatter_plot(sample_meta,
                                         column_x = "n_unique",
                                         name_x = "N Unique Fragments per Cell",
                                         column_y = "peaks_frac",
                                         name_y = "Frac Fragments in Peaks (peaks_frac)",
                                         log_x = TRUE, log_y = FALSE, frac_y = TRUE,
                                         show_targets = FALSE,
                                         color = "orangered") +
                           geom_vline(aes(xintercept = 2.5e3), linetype = "dashed", size = 0.2) +
                           geom_hline(aes(yintercept = cutoffs$peaks_frac), linetype = "dashed", size = 0.2) +
                           ggtitle(sprintf("%s %s", sample_meta$pool_id[1], sample_meta$pbmc_sample_id[1]))
                       })

plot_grid(plotlist = qc_scatter_list,
          ncol = n_grid_columns,
          nrow = n_grid_rows)
```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_fragment_stats_fritss"></a>

#### Fraction of Reads in TSS (+/- 2kb) per Cell
```{r}
category_fritss_violins <- qc_violin_plot(meta_hto,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "tss_frac",
                                         name_y = "FRITSS",
                                         fill = "mediumorchid3",
                                        log_y = FALSE)  
hto_fritss_violins <- qc_violin_plot(meta_hto,
                                         category_x = "hto_category",
                                         name_x = "HTO Category",
                                         column_y = "tss_frac",
                                         name_y = "FRITSS",
                                         fill = "mediumorchid3",
                                        log_y = FALSE)
well_fritss_violins <- qc_violin_plot(filtered_meta_singlet,
                                     category_x = "sample_hto_pool",
                                     name_x = "Sample",
                                     column_y = "tss_frac",
                                     name_y = "FRITSS (Singlets)",
                                     fill = "mediumorchid3",
                                    log_y = FALSE)

fritss_violin_list <- list(category_fritss_violins, 
                           hto_fritss_violins,
                           well_fritss_violins)

plot_grid(plotlist = fritss_violin_list,
          ncol = 3, rel_widths = c(1, 1, 3),
          nrow = 1, align = "h")
```

#### Reads vs tss_frac scatter
```{r fig.width=grid_width, fig.height=grid_height}
qc_scatter_list <- map(sample_filtered_meta_singlet_list,
                       function(sample_meta) {
                         qc_scatter_plot(sample_meta,
                                         column_x = "n_unique",
                                         name_x = "N Unique Fragments per Cell",
                                         column_y = "tss_frac",
                                         name_y = "Frac Fragments in TSS (tss_frac)",
                                         log_x = TRUE, log_y = FALSE, frac_y = TRUE,
                                         show_targets = FALSE,
                                         color = "mediumorchid3") +
                           geom_vline(aes(xintercept = 2.5e3), linetype = "dashed", size = 0.2) +
                           geom_hline(aes(yintercept = cutoffs$tss_frac), linetype = "dashed", size = 0.2) +
                           ggtitle(sprintf("%s %s", sample_meta$pool_id[1],sample_meta$pbmc_sample_id[1]))
                       })

plot_grid(plotlist = qc_scatter_list,
          ncol = n_grid_columns,
          nrow = n_grid_rows)
```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_fragment_stats_fralt"></a>

#### Fraction of Reads in ENCODE/Altius Index per Cell
```{r}
category_enc_violins <- qc_violin_plot(meta_hto,
                                         category_x = "barcode_category",
                                         name_x = "Barcode Type",
                                         column_y = "altius_frac",
                                         name_y = "FRIENCODE",
                                         fill = "darkred",
                                        log_y = FALSE)
hto_enc_violins <- qc_violin_plot(meta_hto,
                                         category_x = "hto_category",
                                         name_x = "HTO Category",
                                         column_y = "altius_frac",
                                         name_y = "FRIENCODE",
                                         fill = "darkred",
                                        log_y = FALSE)
well_enc_violins <- qc_violin_plot(filtered_meta_singlet,
                                     category_x = "pbmc_sample_id",
                                     name_x = "Sample ID",
                                     column_y = "altius_frac",
                                     name_y = "FRIENCODE (Singlets)",
                                     fill = "darkred",
                                    log_y = FALSE)

enc_violin_list <- list(category_enc_violins, 
                        hto_enc_violins,
                        well_enc_violins)

plot_grid(plotlist = enc_violin_list,
          ncol = 3, rel_widths = c(1, 1, 3),
          nrow = 1, align = "h")
```

#### Reads vs altius_frac scatter
```{r fig.width=grid_width, fig.height=grid_height}
qc_scatter_list <-map(sample_filtered_meta_singlet_list,
                       function(sample_meta) {
                         qc_scatter_plot(sample_meta,
                                         column_x = "n_unique",
                                         name_x = "N Unique Fragments per Cell",
                                         column_y = "altius_frac",
                                         name_y = "Frac Fragments in Altius (altius_frac)",
                                         log_x = TRUE, log_y = FALSE, frac_y = TRUE,
                                         show_targets = FALSE,
                                         color = "darkred") +
                           geom_vline(aes(xintercept = 2.5e3), linetype = "dashed", size = 0.2) +
                           geom_hline(aes(yintercept = cutoffs$altius_frac), linetype = "dashed", size = 0.2) +
                           ggtitle(sprintf("%s %s", sample_meta$pool_id[1],sample_meta$pbmc_sample_id[1]))
                       })

plot_grid(plotlist = qc_scatter_list,
          ncol = n_grid_columns,
          nrow = n_grid_rows)
```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_json_out"></a>

### Write QC JSON

```{r atac_hash_Save_QC_JSON}
stm(paste0("Writing JSON to ",out_json))

qc_list_json <- jsonlite::toJSON(qc_list,
                                 auto_unbox = TRUE,
                                 pretty = TRUE)

writeLines(qc_list_json,
           out_json)
```

[Return to Contents](#scatac_hashing_contents)

<a id="atac_hash_session_info"></a>

### Session Information

```{r atac_hash_Session_Info}
sessionInfo()
```

Total time elapsed
```{r atac_hash_Show_Time}
end_time <- Sys.time()
diff_time <- end_time - start_time_atac_hash
time_message <- paste0("Elapsed Time: ", 
                       round(diff_time, 3),
                       " ", units(diff_time))
print(time_message)
stm(time_message)
stm("10x ATAC Batch QC Report complete.")
```

[Return to Contents](#scatac_hashing_contents)  

---  

Hashed scATAC batch QC module `r {scatac_hashing_module_version}`, Lucas Graybuck, Lauren Okada  

```{r scatac_sample_cleanup, include = FALSE}
module_vars <- setdiff(ls(), orig_workspace)
rm(list=module_vars)

gc()

```